\papertitle

### 2014-03-18 final-report/paper.tex
part of intro

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overview\xspace}

@@

@@

The \overall shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.

@@

\subsection{Case 1: Identifying Performance Bottlenecks using the \overall}

@@

\subsection{Case 2: Identifying Data Skew using the \network View}

@@

The \network visualization at a glance shows how much data was sent between workers by one query fragment to the next. The two \network views in Figure~\ref{fig:no-skew} and Figure~\ref{fig:skew} were obtained by selecting the Frag0$\rightarrow$Frag2 and Frag1$\rightarrow$Frag2 edges respectively in the \graph view. Figure~\ref{fig:network} displays aggregate data communication between workers. In Figure~\ref{fig:no-skew} the amount of data sent from each worker to every other worker is balanced as opposed to Figure~\ref{fig:skew} where one can see that the volume of data sent to worker~1 and worker~5 outweights data sent to the other workers in the system. This apparent data skew could be caused by partitioning issues.

\subsection{Case 3: Identifying Execution Skew using the \fragment View}
The \fragment visualization allows the user to dive down into query execution schedules at the worker level.

>>>>

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\overview}{Fragment Overview\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

Database query performance is often unpredictable, specially when the DBMS is distributed. This requires database 
administrators to spend significant amounts of time and effort isolating and debugging the root cause of performance 
problems. These may include skewed data partitioning or run-time issues, such as resource contention or 
adverse network conditions.

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues, 
saving them significant guesswork and programming effort to identify the appropriate logs to analyze.

@@

The \overview shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.

@@

\subsection{Case 1: Identifying Performance Bottlenecks using the \overall View}

@@

\subsection{Case 1: Identifying Data Skew using the \network View}

@@

The network visualization at a glance shows how much data was sent between workers. Figure~\ref{fig:network} compares the communication between workers. In Figure~\ref{fig:skew} one can see that most of the data is sent to worker~1 and then worker~5.
